Results

### 2023-03-03 06_Paper/ER-ED/ERED_Stage2/Results.Rmd
Cross referece for Table 1

Individual SVs could be determined for `r nrow(data_SV)/3` participants for all three ER strategies.
SVs ranged between `r papaja::apa_num(min(data_SV$sv), digits = 3)` and `r papaja::apa_num(max(data_SV$sv))`.
In sum, $n=$ `r  papaja::printnum(sum(data_SV$sv == 1))` had a SVs of 1.0, indicating a clear preference for one ER strategy.
Highest SV for distraction was reported by $n=$ `r  papaja::printnum(sum(data_SV$strat_c[data_SV$strategy == "distraction"] == -1))`, for distancing by $n=$ `r  papaja::printnum(sum(data_SV$strat_c[data_SV$strategy == "distancing"] == -1))`, and for suppression by $n=$ `r papaja::printnum(sum(data_SV$strat_c[data_SV$strategy == "distancing"] == -1))`.

@@

The second model explained `r papaja::printnum(MLM2_r2[2])` percent of variance. 
All results of the second model are in table\ \@ref(tab:TabMLM_H5).

``` {r TabMLM_H5, echo=FALSE, message=FALSE, warning=FALSE}
papaja::apa_table(
  H5_M2_table,
  caption = "Results of multilevel model predicting subjective values of ER strategies.",
  booktabs = TRUE,
  escape = FALSE,
  placement = "H")
```

>>>>

Individual SVs could be determined for `r nrow(data_SV)/3` participants for all three ER strategies.
SVs ranged between `r papaja::apa_num(min(data_SV$sv), digits = 3)` and `r papaja::apa_num(max(data_SV$sv))`.
In sum, $n=$ `r  papaja::printnum(sum(data_SV$sv == 1))` had a SVs of 1.0, indicating a clear preference for one ER strategy.
Absolute preferences for ER strategies were relatively equally distributed.
Highest SV for distraction was reported by $n=$ `r  papaja::printnum(sum(data_SV$strat_c[data_SV$strategy == "distraction"] == -1))`, for distancing by $n=$ `r  papaja::printnum(sum(data_SV$strat_c[data_SV$strategy == "distancing"] == -1))`, and for suppression by $n=$ `r papaja::printnum(sum(data_SV$strat_c[data_SV$strategy == "distancing"] == -1))`.

@@

The second model explained `r papaja::printnum(MLM2_r2[2])` percent of variance. 
All results of the second model are in table\ \@ref(tab:TabMLMH5).

[INSERT TABLE 1 HERE]

``` {r TabMLMH5, echo=FALSE, message=FALSE, warning=FALSE}
papaja::apa_table(
  H5_M2_table,
  caption = "Results of multilevel model predicting subjective values of ER strategies.",
  booktabs = TRUE,
  escape = FALSE,
  placement = "H")
```
